UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-08 files/paper/paper.tex
update

\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

@@

\section{Introduction}
Vision is a commonly used sensor in autonomous underwater robots due to its non-intrusive, passive, and energy
effecient nature. The monitoring of coral reefs \cite{shkurti2012multi}, deep ocean exploration
\cite{whitcomb2000advances}, and mapping of the seabed are all tasks suitable for autonomous robots because they
provide safety by taking the risk instead of a human. Despite the advantages vision provides, many underwater
environments can be quite noisy due to light refraction and particles present in the water. Because red wavelengths are
quickly absorbed by water, images tend to have a green or blue hue to them. As you go deeper, this worsens as more
and more red wavelengths are being absorbed. This extremely non-linear distortion has many factors such as the amount
of light present (overcast vs sunny or depth), particles in the water, time of day, and the camera being used. This may
cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of
color.

@@

\section{Method}
Our approach

@@

>>>>

%\newcommand\animage{\adjustbox{valign=m,vspace=0pt}{\includegraphics[width=.2\linewidth]{n01496331_15872_original}}}

\usepackage{adjustbox}
\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

@@

\section{Introduction}
TODO - talk about having to go back to the same location if you want to get good/bad pairs of the "same" image.
Vision is a commonly used sensor in autonomous underwater robots due to its non-intrusive, passive, and energy
effecient nature. The monitoring of coral reefs \cite{shkurti2012multi}, deep ocean exploration
\cite{whitcomb2000advances}, and mapping of the seabed are all tasks suitable for autonomous robots because they
provide safety by taking the risk instead of a human. Despite the advantages vision provides, many underwater
environments can be quite noisy due to light refraction and particles present in the water. Because red wavelengths are
quickly absorbed by water, images tend to have a green or blue hue to them. As you go deeper, this worsens as more
and more red wavelengths are being absorbed. This extremely non-linear distortion has many factors such as the amount
of light present (overcast vs sunny or depth), particles in the water, time of day, and the camera being used. This may
cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of
color.

@@

\section{Method}
In this section we propose our method for color restoration of underwater images. Depending on depth, lighting
conditions, camera, and location, the amount of distortion an image undergoes can vary.  Because ground truth pairs do
not exist for distorted underwater images, we use the recently proposed CycleGAN \cite{zhu2017unpaired} to generate
a paired dataset of images. CycleGAN has shown success in translating an image from domain $X$ to domain $Y$,
\textit{without} a paired sample. By letting $X$ be a set of underwater images

@@

\begin{figure}
\centering
\begin{tabular}{p{1.7cm} p{1.7cm} p{1.7cm} p{1.5cm}}
   % TODO 
   % I couldn't figure out how to get the text centered above the images
   % Also, the numbers below the images should be centered too, and more
   % obviously below the row instead of seemlingly above the next one. Those
   % numbers are the distances in pixel space (normalized between [0,1]) from
   % the edge image to the original edge image.

   \small{Original} & \small{CycleGAN} & \small{UGAN} & \small{UGAN-P} \\

   \includegraphics[width=0.8in]{n01496331_15872_original} &
   \includegraphics[width=0.8in]{n01496331_15872_cimg}     &
   \includegraphics[width=0.8in]{n01496331_15872_u0img}    &
   \includegraphics[width=0.8in]{n01496331_15872_u1img}    \\ [-1ex]
   \includegraphics[width=0.8in]{n01496331_15872_oedges}   &
   \includegraphics[width=0.8in]{n01496331_15872_cedges}   &
   \includegraphics[width=0.8in]{n01496331_15872_u0edges}  &
   \includegraphics[width=0.8in]{n01496331_15872_u1edges}  \\
   0 & \small{125.78} & \small{80.68} & \small{78.49} \\

   \includegraphics[width=0.8in]{n01496331_22079_original} &
   \includegraphics[width=0.8in]{n01496331_22079_cimg}     & 
   \includegraphics[width=0.8in]{n01496331_22079_u0img}    &
   \includegraphics[width=0.8in]{n01496331_22079_u1img}    \\ [-1ex]
   \includegraphics[width=0.8in]{n01496331_22079_oedges}   &
   \includegraphics[width=0.8in]{n01496331_22079_cedges}   &
   \includegraphics[width=0.8in]{n01496331_22079_u0edges}  &
   \includegraphics[width=0.8in]{n01496331_22079_u1edges}  \\
   0 & \small{94.57} & \small{38.22} & \small{37.29} \\

   \includegraphics[width=0.8in]{n02607072_4739_original} &
   \includegraphics[width=0.8in]{n02607072_4739_cimg} &
   \includegraphics[width=0.8in]{n02607072_4739_u0img} &
   \includegraphics[width=0.8in]{n02607072_4739_u1img} \\ [-1ex]
   \includegraphics[width=0.8in]{n02607072_4739_oedges} &
   \includegraphics[width=0.8in]{n02607072_4739_cedges} &
   \includegraphics[width=0.8in]{n02607072_4739_u0edges} &
   \includegraphics[width=0.8in]{n02607072_4739_u1edges} \\
   0 & \small{100.69} & \small{87.81} & \small{87.95} \\

\end{tabular}
\caption{Running the Canny Edge Detector on sample images. Both variants of UGAN contain less noise than CycleGAN,
and are closer in the image space to the original. For each pair, the top row is the input image, and bottom row
the result of the edge detector.}
\end{figure}
